The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks

### 2024-11-27 paper.Rmd
updated citations

where \( R_0 \) is the initial quantity of the substance, \( c \) is the decay constant, and \( t \) is time. As \( R \) decreases, the propensity function \( a(R) = c \cdot R \) ensures that the decay rate becomes slower over time. This results in a high number of decay events at the beginning of the simulation, which gradually diminishes as fewer molecules remain.

@@

#### Radioactive Half-Life
The exponential decay observed in the simulation aligns with the concept of half-life, a critical measure in the study of radioactive processes. The half-life (\( t_{1/2} \)) is defined as the time required for half of the radioactive substance to decay. It can be calculated as:

>>>>

where \( R_0 \) is the initial quantity of the substance, \( c \) is the decay constant, and \( t \) is time (@Henriksen2002). As \( R \) decreases, the propensity function \( a(R) = c \cdot R \) ensures that the decay rate becomes slower over time. This results in a high number of decay events at the beginning of the simulation, which gradually diminishes as fewer molecules remain.

@@

#### Radioactive Half-Life
The exponential decay observed in the simulation aligns with the concept of half-life, a critical measure in the study of radioactive processes. The half-life (\( t_{1/2} \)) is defined as the time required for half of the radioactive substance to decay (@Henriksen2002). It can be calculated as:
